

\begin{frontmatter}

\title{A Methodology for Determining the Dynamic Exchange of Resources in
  Nuclear Fuel Cycle Simulation}

%% Group authors per affiliation:
\author[iiasa]{Matthew J. Gidden\corref{corref}}
\cortext[corref]{Corresponding author}
\ead{gidden@iiasa.ac.at}
\address[iiasa]{International Institute for Applied Systems Analysis,
  Schlossplatz 1, A-2361 Laxenburg, Austria}
\author[uw]{Paul P. H. Wilson}
\address[uw]{University of Wisconsin - Madison, Department of Nuclear
  Engineering and Engineering Physics, Madison, WI 53706}

\begin{abstract}
Simulation of the nuclear fuel cycle can be performed using a wide range of
techniques and methodologies. Past efforts have focused on specific fuel cycles
or reactor technologies. The \Cyclus fuel cycle simulator seeks to separate the
design of the simulation from the fuel cycle or technologies of interest. In
order to support this separation, a robust supply-demand communication and
solution framework is required. Accordingly an agent-based supply-chain
framework, the Dynamic Resource Exchange (DRE), has been designed implemented in
\Cyclus. It supports the communication of complex resources, namely isotopic
compositions of nuclear fuel, between fuel cycle facilities and their managers
(e.g., institutions and regions). Instances of supply and demand are defined as
an optimization problem and solved for each timestep. Importantly, the DRE
allows each agent in the simulation to independently indicate preference for
specific trading options in order to meet both physics requirements and satisfy
constraints imposed by potential socio-political models.  To display the variety
of possible simulations that the DRE enables, example scenarios are formulated
and described. Important features include key fuel-cycle facility outages,
introduction of external recycled fuel sources (similar to the current Mixed
Oxide (MOX) Fuel Fabrication Facility in the United States), and nontrivial
interactions between fuel cycles existing in different regions.
\end{abstract}

\begin{keyword}
nuclear fuel cycle\sep  optimization\sep agent-based modeling
\end{keyword}

\end{frontmatter}

\linenumbers
