\section{Methods \& Strategies}

\subsection{Modeling Supply \& Demand}

\subsubsection{Agent Communication}

An agent communication interface is used to determine supply and demand. The
communication execution is implemented in phases. First, a request for bids
(RFB) phase is executed to determine demand. Next, and response to request for
bids (RRFB) phase is executed to determine supply.

% RFB, RRFB phases

\subsubsection{Graph Representation}

Supply and demand is then translated into an \textit{ExchangeGraph}, stripping
away any derived \textit{Resource} object specialization. 

% mention separability into req/sup cases

\subsubsection{Mixed Integer-Linear Problem Representation}

In order to solve the MRP with mathematical programming solvers, a separate
translation protocol was implemented to translate instances of an
\textit{ExchangeGraph} into an instance of a mixed integer-linear (MILP) problem
using the standardized Open Solver Interface (OSI). %cite osi

\subsection{Solvers}

\subsubsection{A Greedy Heuristic}

A custom heuristic was implemented that utilizes domain-level knowledge of the
resource exchange interface in Cyclus.

\subsubsection{Linear Programming}

In the case in which partial orders are allowed (e.g., when not explicitly
modeling fuel assemblies), the MILP formulation of the MRP simplifies into a
linear program. Linear programs have very fast solution times. This work
utilizes the COIN Linear Program (CLP) solver.

\subsubsection{Mixed-Integer Programming}

% discuss heuristics, cuts, etc.
This work utilizes the COIN Branch and Cut (CBC) solver. 

\subsection{Test Cases}

Solver performance for MILPs is highly dependent on both problem structure and
coefficient values of a given instance. In the absence of a large number of
instances mined from user-run simulations, test cases must be generated. These
cases are designed to explore the behavior of the model as simulation entity
behavior becomes more precise (e.g., modeling individual assemblies) and the
number of simulation entities grows.

\subsubsection{Reactor Request Case}

A description of the RR case.

\subsubsection{Reactor Supply Case}

A description of the RS case.

\subsection{Analysis Platform}

A discussion of Cyclopts, highlighting notion of parameter space, conversion
from parameters to instances, execution, output, and analysis. 

\subsubsection{High Throughput Computing Execution}

Discuss interaction with condor, highlighting specialized nodes used for timing study.
